Reading Notes

### 2020-07-27 paper.tex
not an outline anymore haha

\documentclass{article}
\title{Reading Notes}

\begin{document}
\title{}

today I got this repo set up. Next time, I'll reskim these papers:

MARTINI\cite{Marrink2007}

VOTCA\cite{Ruhle2009}

TraPPE\cite{Maerzke2011}

and read this: \cite{Chakraborty2018a}

got busy with fancy-ing up the GIXStapose repo, helping rachel, office hours, and atom-typing with gaff-foyer with ryan and chris. Briefly skimmed the chakraborty paper-- they consider all possible mappings that a cg compound can have in order to systematically pick a cging scheme.
OK Chakraborty notes:
-exclude cg mapping schemes to those that maintain symmetry
-Zhang and Voth designed CG mapping operators by preserving "essential dynamics"
-Cao and Voth worked on centering functions COM vs center of charge. They found center of change was better for preserving intermolecular structure.
-Wagner generalize centering functions to arbitrary thermodynamic quantities
-Marrink grouped four heavy atoms and showed that this simple consistent scheme works.
CG models are validated by preservation of rdfs and velocity autocorrelation functions (vacfs)
mapping operator tree

Today I'm reading the VOTCA\cite{Ruhle2009} paper with the goal of answering these questions:
how do they choose a chromophore?

how do they calculate the transfer integral?

how do they do backmapping?

other notes:
CG methods--IBI, force matching, inverse MC. This paper goes over details of these and how they're implemented in votca. This wasn't really what I wanted to read about so I skimmed.
They use ESPResSo++ for quantum calculations
OK, this isn't the right paper to read about CT stuff or backmapping. Let's look at some of these [http://www.votca.org/citations/using-votca](http://www.votca.org/citations/using-votca)
Also I'm noticing in this list of papers--Marrink (cited by chakraborty) is here and there is a paper mentioning the importance of side-chains for charge-mobility! \cite{May2011}
Next time read about tie-chains \cite{May2011} and/or charge mobility \cite{Lukyanov2010}
Lukyanov--sounds a lot like morphct, gaussian density of states? I thought their (votca's) method was like morphct but now I'm not sure... It seems like they're using a simplification and not doing dft.

https://pubs.acs.org/doi/10.1021/ja104380c - 
rubrene record charge carrier $15 \frac{cm^{2}}{(V s)}$ single crystal by vapor deposition. typical for thin-film is $1 {cm^{2}}{(V s)}$

good discussion of some of the assumption of marcus theory. 
Drude model (electrons bounce off stationary nuclei like a pinball machine) works for perfect crystals at low temp.
At RT it doesn't work. Marcus theory assumes nuclear dynamics much slower (Borne-Oppenheimer) and electronic coupling is weak (what does this mean exactly?). Static disorder is based on the electronic DOS and the hopping rate between localized states. (As opposed to what?)
They start with single crystal structures from xray data. They calculate reorganization energies with b3lyp 6-311G(d,p) and transfer integrals with ZINDO. (check their SI)
How are they able to calculate direction-resolved transfer integrals?? very cool. What exactly do the transfer integral graphs mean? (Figure 2) Had a helpful chat with Chris about this and it helped me to think through the figures. The y-axis on the transfer integral is counts and the x-axis is energies--it makes sense that movement of an electron in different directions would require different energies and/or be more likely. Still not sure how to calculate it though.

\cite{Vehoff2010a}

rubrene record charge carrier $15 \frac{cm^{2}}{V s}$ single crystal by vapor deposition. typical for thin-film is $1 \frac{cm^{2}}{V s}$

Today I'm digging around in more of the votca stuff to try and figure out how to run kmc there. They use ORCA too! Also their tutorials and documentation REALLY SUCK. [https://github.com/votca/xtp-tutorials](https://github.com/votca/xtp-tutorials) in particular I'm looking at LAMMPS/KMC\_Thiophene.
OK. either I am dumb or that tutorial sucks. I can tell that they're using orca and the inputs/oputputs the use but there's no explanation of what they're doing. It looks like they calculate the reorganization energy, but they don't define a chromophore--which makes sense for thiophene but what about when your molecule is ginormous?

\cite{Ruhle2011b}

discusses charge transport in amorphous films of [tris-(8-hydroxyquinoline)aluminum](https://en.wikipedia.org/wiki/Tris(8-hydroxyquinolinato)aluminium). Oh Figure 1 is nice--it is a workflow of what can be done in votca.
11A talks about how to parameterize new contributions to a force-field using first-principles.
11B choosing a "chromophore"-- rigid fragments vs conjugated segments. they broke apart the chromophore in a polymer like p3ht using the dihedral angle--although they validated this choice with other methods. Interesting-- they replace the chromophores with those which have been geometry optimized using DFT. then they make a neighbor list
I'll come back to this paper later. I at least was able to answer some of my questions about choosing a chromophore.
11C talks about calculating the transfer integral for each pair and why ZINDO works and when it breaks down.

rereading the perspective paper \cite{Jankowski2019} looking for things to read next:
Braun 2018 foundations in molecular simulation
https://doi.org/10.33011/ livecoms.1.1.5957
74-89 are relevant to coarse-graining
92-95 start here for opvs

Today I'm thinking about some of the big picture stuff related to my proposal:
Science-wise I am thinking of my proposal like this: Humans use energy and burning fossil fuels to get that energy really sucks. rising CO2 concentration in the atmosphere contributes to global warming. Sustainable, low-carbon footprint energy generation is vital to protect the precious climate which sustains all life. Energy generation using OPV devices is one form of alternative energy. But there are a lot of potential OPV molecules out there! So how can we develop inexpensive, fast methods for screening this ZOO of compounds? Well we can use modelling techniques and a computer. Computational simulations of organic photovoltaics suffer from a problem of length scales: OPV morphologies can have bulk features on the scale of 10s of nanometers (BHJ, exciton dissociation length, pi-stacking) which affect the morphology, yet still we are interested in the electronic properties of this system--a fundementally quantum mechanical property--taking place on the angstrom scale where with current computers we can only realistically look at up to 100's of atoms. <so we break apart the problem MD to get a morphology, Zindo to calculate energy splitting of neighbors-->transfer integral, KMC to estimate CT, talk about results of evan/matty/votca> What am I going to add? more robust/automated coarse-graining and backmapping, calculation of reorganization energy, chromophore detection.
Things I care about: The environment--I like working on a project that theoretically could help find the next molecule for OPV technology. Sometimes it seems very far removed, but having sustainable technology as an ultimate goal matters to me. I also care a lot about help make science more accessible to everyone: I find myself really excited about creating tools which help to visualize the unseeable and to communicate complex ideas in a simple understandable way. I'm not sure this has anything to do with anything, but it's definitely a developing passion.

I'm also reading this paper today https://arxiv.org/pdf/2003.02031.pdf which is a bout TRUE simulations.
notes:
GUI's hurt reproducibility, MS Excel hides the formula's and order of calculation (p 4)
poorly documented code and raw data files dont help reproducibility (looking at you votca) (p4)
*I want to include start to finish notebooks with any paper I publish...* Also docker containers with my exact software stack.
I love the examples in this paper :) It feels a lot like our perspective paper! I'm skimming them but I love that notebooks are included in the SI.
They qualify the GUI's are bad statement saying that GUIs are only bad *if they hide the workflow details.*

Matt Thompson got a job at OpenFF, one of the tools they list as desirable for applicants is knowledge of psi4:
https://pubs.acs.org/doi/abs/10.1021/acs.jctc.8b00286

read official papers for mosdef. check github.

Reading

\cite{Hanson2016}

also my mendeley overwriting my files because it thinks they are duplicates or something? It keeps losing the pdf even though I've uploaded it. :(
SMILES - simplified molecular-input line-entry system
SMARTS - smiles arbitrary target specification
around since 1980s
alternatives SLN, MQL, CSRML.
This paper is about specifically Jmol smiles so I'm skipping to a different one.

\cite{Weininger1988}

First paper about smiles- how do we unambiguously represent a chemical structure? historically CAS, graph theory, IUPAC.
human-readable and machine readable
hydrogens, single bond don't need to be specified. designed for organic molecules.

\cite{Smith2018}

reading about psi4: free and open source with python api that uses blas and c under the hood. has jupyter notebooks tutorials. This paper reads like our perspective paper in tone :hearteyes: 2.2 -2.3 kinda lost me. I should look at their jupyter notebooks.

Today searched "coarse grain backmapping" in the library and got the following papers:

\cite{Alessandri2017b}

Coarse graining in OPV bulk heterojunctions! p3ht and pcbm, solvent evaporation. morphologies need large interfacial area between donor and acceptor and relatively high crystallinity and connection to the electrode.How can we investigate the processing conditions that achieve the highest performance?
Analysis of OPVs include AFM, SEM, TEM - provide info about interpenetration (how the two phases are dispersed.) Electron tomography can study 3d morphology., but has limited contrast in organic material due to low scattering. GIXD, GISAXS quantifies the degree of crystallinity but averages over the structure. 
CG allows us to look at these systems but CG models are currently not transferrable meaning that for each new system a new CG model must be developed which is slow. Simulated annealing is often used but a more relevant to experiment method is simulated evaporation.
This paper used CG model like Lee and Pao (read this paper) but also based on finer model like martini. Martini does backmapping. (backwards.py) 
They use explicit solvent (CB/benzene) and they remove molecules randomly as the simulation progresses. Longer drying time results in larger crystallites/ fewer D-A contacts. P3ht shows backbone (pi-pi) stacking at a distance of 4.5 A in the CG morphology. They use backwards.py to do their backmapping. They use 3 beads to represent thiophene in p3ht with no explicitly anisotropic interaction. Carillo (ref 26) used anisotropic addition onto very simplified model (thiophene is single bead) of lee (ref 22). (read these) The model used here thiophene is a triangle and they think this helps it stay planar and stack.
Figure 5 is beautiful.

\cite{Haxton2015a}

CG beads with orientation. They use the word "stiffest" to describe degrees of freedom--they mean bond stretching, angle bending, and torsion within rings. They suggest there are two separate ways to improve CG: better mapping between AA and CG or better CG interactions. The seconds can be helped with IBI, entropy minimization... First one is what the authors will focus on.
Point-site method maps groups of atoms onto a bead--bead potential is spherically symmetric, but some models use neighboring sites to introduce some directionality. e.g., Alemani et al created a protein model where the dipole interaction was a function of the alpha-carbon angle. Here they add orientation to the point-site model. This increases the degrees of freedom for each site from 3 to 6, but they model bonds and angles as stiff and dihedral angles (except rings and double bonds) as soft. They also map about 8 atomns to a site. They use backmapping from ref 64--not backwards.py. 
They simplify the ideal interactions of the CG model (many-body problem) to pai potentials. They show how to calculate to error in an observable calculated on backmapped structure. C code used for backmapping in SI.
mapping ratio - atomic DOF / CG DOF. PRIMO on average is 3.0, UNRES, MARTINI, MS-CG are 8.2, 7.1, and 6.0. I think this paper aims to improve on PRIMO by adding directionality? they measure accuracy with rmsd and efficiency with mapping ratio.

\cite{Wassenar2014b}

This paper is about backwards.py. The authors are from university of groeningen where GROMACS is made. however this tool is generic and not specific to gromacs. it uses geometric projection and position restrained MD relaxation--same as what Matty did. can map between anything just needs a mapping.
Good overview of CG methods:
Rzepiela - randomly place atomistic beads on small spheres around CG beads. Requires many steps, specific to one verison of GROMACS, but can be made specific with correspondence between atoms and beads.
Brocos - lipid micelles. placing atoms on a trace through the CG bead and adding peripheral atoms at offset. 
A good CG model should yield correct structures and be simple quick and flexible. Should be generic (ff and system type) and require little information. Then information provided should be the CG coordinates, the atomistic topology and the correspondence mapping between the atomistic and CG particles.
They go from MARTINI-CG to GROMOS 54a7 UA to CHARMM36 AA.
Some matrix mapping that I don't totally understand. Confusing between A the matrix and A the atom position. :/
Fig 5 is neat! c: shows a helical protein at each step of the CG->AA process. their procedure appears to improve upon the simulated anealing of rzepiela. 
* look at backwards.py with the intent of better understanding the Matrix transformation.

\cite{Peng2019a}

biomolecules. Backmapping based on Bayesian inference and restrained MD. cgmap.py -- they tell us the names of their codes but don't provide them?? They try multiple CG methods: Martini (twice with different initial structure), UNRES, ENM. Martini had the lowest RMSD but it is also the finest grain method. They have an ultra coarse method that only use 5 beads for a small protein; it gets impressive results (RMSD 0.47 angstrom) for how sparse it is! But it is not sufficiently accurate to predict structure-- other RMSD > 10angstrom. their method is more expensive. I don't quite understand how they get some of the probabilities for the Bayesian part, but my takeaway from this paper is that the logrestraints work a lot better for them and Bayesian inference, although expensive, allows them to skip the AA MD simulation at the end?

\cite{Rolland2020a}

This is the paper we reviewed in lab meeting! CG -> backmap -> mobility. AA MD can reproduce XRD patterns pi-pi stacking, formation of lamellar structure, change in morphology at high oxidation levels, mobility dependence on chain-length (* looks into ref 26 and compare to evan's tie chain paper)
CG allows us to look at larger lengthscales and with backmapping we can restore atomistic details, but is there a cost? ref 44 model HOTT molecules as ellipsoids with Gay Berne interactions (I'm thinking of this as anisotropic--i.e., directionally dependent so good for ellipsoids--Lennard Jones. Often used in liquid crystal systems.) 
They use the same backmapping as us ref 13. Many CG papers verify by XRD buyt they claim same XRD can result in very different mobility. ref 26. They use Wassenar's backward.py script. -- He is from the university which makes GROMACS
CG overestimates density--backmapping fixes it. XRD of backmapped AA match AA. pipi stacking is corrected and lamellar structure present. Mobility also good. They explain the differences between the AA and CG mobilities saying that the AA one is smaller so it's a size effect due to over estimated percolation threshhold--i.e. the connectivity is overestimated because the periodic volume is small enough that the periodic image has an effect.

\cite{Poblete2018a}

RNA - backmapping steered MDaimed at minimizing a particular RMSD (ERMSD) between atomic and target structure. target structure were found to be recovered by this backmapping except in the case where there were unpaired bases. folding pathway dependent on parameters used in ERMSD.
need AA strutures to validate with experiment (x-ray or neutron scattering) backmapping usually involves placing atomistic coordinates relative to the beads and then minimizing the energy of the structure using steepest descent or short MD runs (could use position restraint). Atomistic can even be mapped onto the whole trajectory. 
This work describes the backmapping of the SPlit and conQueR (SPQR) method. Minimizes the ERMSD distance between solvated AA strand of the CG structure (RNA). ERMSD : origin is set to CoM of C2 C4 and C6 atoms of each base (see ref 23), then for each pair of bases, rij is the center of base i in the coord system of base j. In order to account for anisotropy, the scaling for the z-direction is different (does this mean the strand is oriented to z in some way??) This metric shows the difference between arrangement of nucleobases of two RNA structures. Backbone and sugar interactions are unrestrained. The paper will show results on the backbone conformation. They use steered MD with ERMSD as the steering parameter. (How does steered MD work?) Look like they use and external pulling force which depend on ERMSD.

Of these the Alessandri paper was the best and  most interesting/relevant. I am pulling some refs from here for next time:

\cite{Mikhnenko2012}

Exciton diffusion length (EDL) in narrow bangap polymers. photoluminescense decay time is related and measurable. PCBM and PCDTBTs modeled with Monte Carlo--code available. They used P3HT as reference (5.4+/-0.7nm exciton diffusion length). 
Exciton diffusion is essential for organic solar cells. excitons are electron hole pairs created by excitation due to light absorption. they are separated into free charges at an interface which creates current. the movement of the excitons through hopping is what is refered to as diffusion. Exciton diffusion length is a factor in device efficiency.
Other methods to measure EDL are fluorescence quenching - the dependence of the exciton quenching efficiency vs semiconductor thickness is fit to 1D diffusion equation. Pros: direct measuremnt, cons: difficult experimentally and there are many things to consider in the model (FRET, effect of polymer-vaccuum interface, optical interference). 
This paper uses MC to model PL decay.
(Losing focus come back tomorrow)

Ugh. I think I've finally fixed my Mendeley library?

\cite{Scharber2013}

Review of state-of-the-art OPV BHJ solar cells. 
pros: thin/light, semitransparent, cheap, continuous production process, short payback times, easy to integrate into new and existing products. 
History of development from 2001 2.5\% PCE to 2011 10\% PCE. Most degrade when exposed to air and sunlight within a few years. Molecular structure including side chains affects stability. Electron affinity of the acceptor determines degradation rate of the semiconductor. Changing the elctrode and using the inverted design(? read waldauf) helps the electrode oxidation. This requires no vacuum
They discuss BHJ morphology and how the A and D regions need to be small enough that an exciton could find it's way to an interface but not so small that once the charge is separated and current is generated at that interface that the current couldn't get to the electrode. The ideal is an interlocked comb structure but in reality solution processed OPVs form patches. This review is not about morphology (they recommened Hoppe2004). Morphology can only effect the efficiency of an AD pair, not the ultimately efficiency limit. This depends on the bandgap and electron affinities of the DA moeities.
fig 5 explains inverted design a bit. 
They discuss costs and efficiencies. Should probably read about Shockley Queisser Limit. (ref 47) based on analysis of pn solar cell they say the max efficiency is 30\% and the optimum band gap in 1.1 eV. Archer and Bolton roughly confirm this -- much of the light energy is lost because the photon is too small to excite the absorber, other loss is due to intraband thermalization of charge carriers (?), 12\% entropic loss, 1\% radiative recombination. Assumption of the Shockley Queisser limit
1. each absorbed photon generates and e/hole pair
2. perfect charge collection
3. radiative recombination as the only recombination.
Based on this work and the external radiative efficiency (ERE) proposed by Green, and actual max of 15-16\% efficiency is predicted.
(continue from 5)

\cite{Waldauf2006}

Read this with intention of understanding inverted design

\cite{Hoppe2004}

Overview of organic solar cells. sp2 hybridization of carbon is what allows organics to absorb in the uv-vis range. (conjugated pi orbitals.) In comparison, inorganic semiconductors have low mobilities but very high absorption coefficients. The exciton diffusion length is shorter in OPVs too.
Most OPV are hole conductors and have band gap around 2 eV, which is higher than silicon. But the ability to modify and tune the chemistry as well as the cheap, mass production makes OPVs enticing.
history: 
first OPVs were single organics layers sandwiched between two metals with different work functions. (Evac - Efermi) 0.7\% PCE
next bilayer heterojuctions-- two organic layers between electrodes (e.g. perylene and phtalocyanine) 1\% PCE
C60 introduced, polymer fullerene bilayer heterojunction.
Bulk heterojunction 2\% PCE
(This article only discusses up to 4\% PCE and does not provide specific explanation for the increase)
common structure is hole-conducting polymer with electron acceptor (C60 as in PCBM). Solution processable due to side chains. Preferential orientation of polymer backbones parallel to the substrate gives rise to anisotropic CT. In BHJ cells CT is sensitive to the morphology.
OPV energy generation steps: 
1. absorption
2. exciton diffusion
3. charge separation
4. charge transport
PCE depends on # photons absorbed, dissociated, and that reach the electrode. Number absorbed depends on the absorption spectrum, absorption coefficient and layer thickness. The fraction of excitons which dissociate depends on the exciton dissociation length and the charge separation probability at the interface. Finally the the number of charges which reach the electrode depends on the driving force or gradient resulting from the potentials of the elctrons and holes. thin films (<100nm) are usually field drift dominated others have enough screening are dominated by concentration gradients at the contacts.
I skipped over devices.
concepts for improvement:
metal electrodes quench electrons in C60 so an transparent, exciton-blocking layer is between electrode and layer with C60. ultrathin LiF interfacial layer is one example. 
Increase the absorption range. smaller band gap <2eV ~800-900 nm.
morphology controls. to control size of fullerene domains in p3ht/fullerene, a plasticizer was added. This increase miscibility of polymer and fullerene creating smaller domains. Solvent/evaporation time, surface interaction, and annealing all have a large effect of the morphology.

\cite{Scharber2006a}
Design rules for donor in BHJ solar cells
interpenetrating network of C60 and conjugated polymer have shown ultrafast charge transfer (~40 fs). There is no competing decay process in this timeframe. optimized mixture with C60 converts absorbed photons to electrons with efficiency close to 100\%. At time of publishing best PCE is ~5\%. Efficiency is limited by low open circuit voltage of device under illumination. Organic semiconductors with bandgap of 2eV are used but observed $V_{oc}$ is in the range of 0.5-1 V. $V_{oc}$ in a metal-insulator-metal is equal to the work-function difference of the two electrodes. In polymer-fullerene $V_{oc}$ is affected by the morphology of active layer, electrochemical potential of the cathode. Ref 15 (Gadisa) studied correlation between electrochemistry andVoc of  polymer fullerene with PCBM and polythiophene and found that variation of the oxidation potential of the polymer caused variation in the photovoltage. (This is not the same as $V_{oc}$ ?) This paper suggests that Voc is related to HOMO of the polymer. and thus the maximum efficiency can be predicted.
I am confused by a lot in the paper and don't understand why Voc is the limiting factor. Fig 2 is interesting, shows how they predict PCE from HOMO/LUMO and bandgap. Should Eg (bandgap) be LUMO acceptor - HOMO donor?
OK so they don't really give suggestions for what kind of chemistry makes a better donor, but they do say that measuring the HOMO of the donor can tell a lot about the PCE of the device.

\cite{Yu1995}

Older paper about BHJs. (is this maybe the first about ADA BHJ?) MEH-PPV efficient charge transfer result from bicontinuous network
time scale for CT from donor to acceptor is <picosecond, $10^{3}$ x faster than radiative/nonradiative decay, so efficiency is near 100\%. Just adding 1\% C60 increase photoconductivity by order of magnitude.
conversion efficiency in a bilayer heterojunction device is limited when photoexcited exciton can't get to the interface. So an interpenetrating network is ideal because it maximizes interfacial area and minimizes the distance and exciton must travel to reach an interface.and if the network is bicontinuous then transfer of the charge to the electrode should be just as efficient.
ITO (indium tin oxide) I thought was to prevent the active layer being quenched by the metal but they're saying it's the anode? PCBM is a soluble C60 derivitive. Ca electrode used.
Pure MEH-PPV Voc 1.6V is consistent with the difference in work function of Ca and ITO. In the MEH-PPV/PCBM mix the turn on current shifts lower by 0.8V thus LUMO of PCBM is 0.8eV below Efermi of Ca. 
They predict greater efficiencies if the morphology is optimized.

\cite{Halls1995}

another older paper. Cavendish lab! Photovoltaic effect - production of electrons/holes under illumination. Molecular semiconductors produce excitons instead of free charges. Charge collection requires dissociation, which is efficient at interfaces of different electron affinities and ionization potentials. (electron goes to larger electron affinity and hole to lower ionization potential.) A layered structure then seems ideal, but Exciton diffusion length is much shorter than the absorption depth. so an interpenetrating network is shwon in this paper to be ideal.
poly-phenylenevinylene derivitive mixture MEH-PPV and CN-PPV. spin coating on glass slide. they claim phase separation on the scale of 10-100nm this measurement relied on ferric chloride doping MEH-PPV but not the CN derivitive.
The current vs Voltage graph for the mixture was very different under illumination.
they predict these sort of flexible polymer photodetectors will be useful in medical imaging.

\cite{Gartner2019a}

>>>>

# what has been done
<should I start with simulation in general?>
<start with what simplifying assumptions MD already makes>
##coarse graining
Coarse-grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models.
Coarse-graining refers to grouping atoms in a structure into a "super-atom" and using an effective potential to represent the resulting coarse grain site.
The resolution of coarse grain systems is broad:
Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible \cite{Paul1995a, Yang2006a,}.
Other goarse-graining schemes may group functional groups together <cite> or even represent an entire amino acid with a single site <cite>.
General coarse grain models of opv thiophene polymers where only the spacing, regioregularity of the side chains were varied were able to predict different order disorder transitions and calculated scattering patterns of these simple systems were comparable to those obtained from experiment \cite{Jankowski2013, Marsh2014} 
A coarse-grain model for phospholipids has allowed for bilayer formation from an initial random configuration to be observed even though the model was parameterized to the vapor-liquid phase transition.\cite{Shelley2001}
Which model is right depends on the length and time scale on which the property of interest can be observed.

For many systems, however, we are interested in properties which span length scales.
For instance, in a system like a opv polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5-10 nm)<cite> -- it is the wrong tool for the job.
If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily--a process called backmapping.
In the same way that a coarse grain model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse grain structure.
The large length scale, polymer level properties can be equilibrated during the coarse grain simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores and the connectivity of these chromophores over distances proportional to the exciton dissociation length.
<what stands in our way?>

<coarse-grain models are specific>

<segue from automated creation of forcefields to...>
<mapping operator has to be decided by hand> <is this section too big?>
Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and where in the site is placed relative to the atom group.
Mapping operators are chosen based on desired resolution of the coarse grain system and the information to be extracted.
A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together--this is the method used in the MARTINI force field\cite{Marrink2007}.
In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
When parameterizing a new molecule you must pick a mapping and then compare the resulting beads to existing beads--a process which is time consuming and error prone\cite{http://www.cgmartini.nl/index.php/tutorials-general-introduction-gmx5/parametrzining-new-molecule-gmx5}.
The MARTINI force field was first designed for lipids--further parameterization for proteins and nuclei acids have been added<cite--and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.
Many mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?<cite any model where rings are one bead> What groups have the most dominant interactions in this structure <cite dna cg model>).
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
There have been efforts to create mapping schemes for automating the process of deciding which atoms are grouped in a "super-atom" bead.
One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function \cite{Chakraborty2018a}.
Another mapping scheme uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the "expert" mapping chosen using chemical intuition reliably\cite{li2020}. 
A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.

<how cg potentials have been obtained>
<IBI>
<why are IBI potentials not transferrable? the RDF is a property of the ensemble average at a given statepoint so the potential derived from this property is also limited.>
separate potentials are required to capture solid and fluid structures of a pure simple lipid <Moore2014 ref 46>
<IBI potentials are sometimes transferrable and it is not clear why sometimes they are and sometimes they aren't.> \cite{Moore2014}

Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential.
\cite{Moore2014}
The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest.
This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid.

When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
If this overlap region is large, there are many potentials which will provide matching RDFs.
For some systems there may not be a potential that represents all states-- this is not unique to coarse potentials, atomistic potentials also have this limitation.

TraPPE fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}
<Talk about what exists and why it is not enough>
<votca, Peng2019a> 
Versatile Object-oriented Toolkit for Coarse-graining Applications (VOTCA) \cite{Ruhle2011b}
includes a coarse-graining, forcefield creation with reverse MC or IBI, and back-mapping modules.
It also allows for charge transport calculations using KMC similar to MorphCT <cite>

reproducibility crisis.\cite{Cummings2019} \cite{Thompson2020} (TRUE paper) poorly documented code and raw data doesn't help.

instead example workflows with docker containers to build software stack.
help make science more accessible and reprodicible.

<compare VOTCA's backmapping to my proposed scheme>
VOTCA makes some progress towards a TRUE simulation pipeline: they include a docker container with their pre-built software stack and example input files <see https://github.com/votca/votca -- using this code via docker> (but some of these input files don't work and the codecoverage on their repo as of time of writing is 0\%), and while including example inputs is a good first step, very little walkthrough (aside from code comments buried in the xml) is given.
A manual is provided but there is some disconnect between the example files and those given in the manual <https://github.com/votca/csg-manual/releases>.
the code is a mix of C++, shell commands, python, and interacts with compiled programs through the command-line and mpi.
which makes their working a little tenuous.
And judging by the amount of confusion in their mailing list <https://groups.google.com/forum/#!forum/votca> there is room for improvement in the API.
Overall though this is program has many features, interfaces with many popular MD engines (lammps, gromacs, hoomd), and is under active, collaborative development.
A good question might be if I'm so into OSS and collaboration--why don't I just contribute an MSIBI package to VOTCA.
This is a reasonable question.
The answer is because I find VOTCA to be near-overwhelming in it's scope and the cognitive load of trying to fit this whole project into my brain is not ideal.
I also don't like their API.
by choosing a pure python API I will be able to make use of jupyter notebooks which can be run on cloud servers using tools like mybinder <link mybinder, link to tutorials I;ve made> which can combine executable code with markdown text and images.
In this way a tutorial can provide exact commands needed to reproduce the example intimately connected with the rationale and justification of that example.
I would like to think that my code speaks for itself, but after reading other people's code, I have a renewed appreciation for explanations in paragraph form, diagrams, and figures.

For an example of what I mean by cognitive load, let's compare an example of my proposed coarse-graining scheme to VOTCAs.
In the following example we will take a hexane molecule and map it to three coarse grain sites (two carbon atoms per site).
VOTCA uses an xml file to do this:
<insert hexane.xml>
It may be easy to think that because what we are doing--mapping two carbons and their attached hydrogens to a single bead so that six alkyl carbons becomes A-B-A--that the process will also be simple.
In order to specify a bead-mapping, we need to know the residue number, the residue name, and the atom name.
For a six atom system this is not too bad, but this could get tedious and error-prone for larger systems.
And keep in mind that these xml files need to be created manually for each compound which is backmapped.
VOTCA's scheme also requires that you specify the bonding and the angles resulting from those bonds, another process which is tedious, error-prone, and probably unecessary--I will discuss this more after discussing my scheme below:
\begin{lstlisting}
hexane_sites = [("_A", "CC[H3]"), ("_B", "CC")]
\end{lstlisting}
The result of using this code in the `coarse` function <link to grits> is a three-site hexane model A-B-A.
The mapping here is specified as a list of bead name / smarts string pairs.
Although they do add some element of cognitive load, SMARTS strings are designed to be human and machine readable and can match atoms based on their chemical environment.
With this scheme, there is no need to look up the name or number of each residue, I simply specify that want two alkyl carbons (CC) requiring that one be a termial carbon by including that it has three attached hydrogens (C[H3]).
The bonding and angles of the resulting coarse grain beads is then inferred based on the bonding of the mapped atoms.
There are even benefits to the mapping being inline with the code:
This allows the user to see the mapping as they progress through the workflow without having to search for multiple files and it may prevent common errors caused by manual file IO such as operating system specific line endings or whitespace characters like tab or space being treated differently.
Having the mapping in-line with the workflow also allows for the user to check that the mapping is correct with built in interactive visualizations, which can display the mapping as an overlay.

We do not propose a new automated mapping, but instead a way to make the mapping and backmapping process easier for the user.
Simplified Molecular Input Line Entry System or SMILES \cite{Weininger} was designed to represent organic molecules in an unambiguous way (similar to IUPAC) but in a line-entry system which is also readable by a computer.
This makes it a good candidate for specifying a coarse-grain mapping scheme.The open-source package, Openbabel, allows for a SMILES string to be converted to a chemical structure and vice versa.
<cite openbabel,SMILES, SMARTS> SMARTS is similar to SMILES but instead of representing a single molecule unambiguously, it has multiple wildcards which can be used for pattern matching.
This pattern matching is also implemented in the Openbabel package.
If we know the SMARTS string for any given CG mapping we can map the CG site to it's center of mass or geometric center.
I have developed a minimum working example of how this can be done <cite grits> and then how the atomistic structure can be recovered.
It could be fairly straightforward to implement a lookup to check if bead parameters already exist--say for the MARTINI model-- by going through and writing out the SMARTS pattern for each existing bead type.
An initial headache that could make parameterizing new compounds for the MARTINI method more foolproof.

<coarse-graining, backmapping, charge transport>

# what remains to be done

# Why should the work be done?
# what specific problems will it solve?
In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
Simulation also helps to give us insight into the atomic interaction which drive self assembly.
A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
The electronic properties are important for light absorption, charge transfer <morehere>
while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
<interfacial area and connectivity>

# how will the work be done?
- I will build on existing tools (signac,freud,mbuild,foyer,tim moore's msibi)
- create signac workflow which takes equilibrated atomistic trajectory (maybe checks if it's equilibrated?) maps the CG beads to it, runs IBI, gets tabulated FF, creates larger CG sim, runs it, does backmapping, then could do: RDF, charge transport, diffraction...
if this workflow is streamlined--it can be applied to many different compounds allowing for us to compare the analyses between our zoo of compounds.
- maybe the workflow could even involve getting the equilibrated trajectory (atomtyping/fill box/run) with the new hoomd 3 api we could even set decorrelation time as a stop trigger...

# what have you accomplished already? what remains?
- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
 this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
using these tools will help me to me a more efficient developer.
It's also helped me to learn how to work as part of a team.
 - created MWE of coarse-graining and backmapping with smiles-- these will need furthertesting as we try them on different compounds but the proof of concept is there.
 - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
 - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
- started development on UFF repo for foyer.
This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
(atom typing is a pain)

#what is the timeline?
#what answers will be immediately forthcoming?
#what additional major research will result?

#will the work involve an outreach component?

#Intellectual merit and broader impacts?
